Embedded Domain Specific Languages inside Functional Languages

### 2014-03-13 paper.tex
Closing arithmetic

@@

About running the code.

About 3 main tricks; functions, recursive values, and statements.

\subsection{How to extract a deep embedding from a Function}

>>>>

\begin{figure}[!t]
  \centering
        XXXX
  \caption{Shallow and Deep Embedding of Arithmetic}
  \label{fig:counter-pictureX}
%  \vspace{-0.1in}
\end{figure}

Figure~\ref{fig:deep-dsls} illustrates the differences between shallow and deep DSLs,
and how a deep embedding combined with a specific run function gives the same result.
For a deep embedded DSL, the run function restores the capability of the shallow
embedding, but another function takes the embedded structure, and uses in in some creative way.

There are many places this design pattern can be used. One example is the specification
of surface textures as functions; it is possible to export these into code executable
on GPUs, simultaneously lifting the abstractions used to write textures, and speeding
up how fast a shallow embedding of the same operations would run.  There is nothing
that is specific about Haskell, or even functional languages here. Indeed, the same
ideas have been used in Java, for a VHDL generator. Haskell, with its powerful abstractions,
allows deep DSLs to be more than just function calls, and almost feel like a straightforward
shallow embedding.

In order to make deep DSLs practical, there are three folklore tricks that are used.
First, we can capture functions, by using dummy arguments. Second, we can observe loops,
buy using observable sharing. And finally, we call observe imperative statements,
by using normalization. We will overview all these tricks, before concluding
with shortcoming and remaining challenges.

\subsection{How to extract a deep embedding from a function}

@@
